A generalized definition of multidimensional item response theory parameters

### 2024-09-03 output/paper_draft/paper_M2PLM_parameters.Rmd
Adds statements and declarations
Change figure output to SVG

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  message  = FALSE,
  cache    = FALSE,
  dev      = "png",
  dpi      =   900,
  dev.args = list(type = "cairo-png")
)

@@

>>>>

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  message  = FALSE,
  cache    = FALSE,
  dev      = "svg"
)

@@

# Statements and Declarations

## Ethical considerations

Not applicable

## Consent to participate

Not applicable

## Consent for publication

Not applicable

## Declaration of conflicting interest

The author(s) declared no potential conflicts of interest with respect to
the research, authorship, and/or publication of this article.

## Funding statement

Not applicable

## Data availability statement

Not applicable
